Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola

### 2022-09-26 Manuscript/supplemental.tex
Worked on SH revisions
Finished comments from SH

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{../Figures/FieldLocations.png}
    \caption{Map of sampled fields, showing locations of 29 commodity canola fields (14 during 2014, 15 during 2015), and 35 seed canola fields (15 during 2015, 20 during 2016). Seed canola is grown only in southern Alberta, while commodity canola is grown across both the northern and southern regions.}
    \label{fig:fieldMap}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{seedfieldBays.jpg}
    \caption[Hybrid seed field near Rainer, AB]{Hybrid seed field near Rainer, AB, showing the outlines of male and female bays in the foreground, with orange leafcutter bee shelters stationed throughout the field. The linear structure on the horizon is the central-pivot irrigation sprinkler.}
    \label{fig:seedfieldPhoto}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth,keepaspectratio=true]{seedfieldPlots.png}
    \caption[Plot arrangement for surveys in hybrid seed fields]{Plot arrangement for surveys in hybrid seed fields, showing hypothetical arrangement of leafcutter shelters ($\Delta$), and male-fertile (\Hermaphrodite) and female bays (\Female) at 5m from the edge of the field. Plots were placed 5, 20, 100, and 400m along a transect (dashed line) from the field edge nearest to the set of honey bee hives. Plots were placed side-by-side in the male bay and edge of the female bay (``edge" plots), and at the 5m and 400m distances, a plot was placed in the centre of the female bay (``centre" plots).}
    \label{fig:seedfieldPlots}
\end{figure}

\begin{table}
\caption{Summary of variables used in structural equation models.}
\centering

\begin{tabular}{l|l|r|r|r|r|r}
\hline
Field Type & Variable & Mean & Median & SD & Min & Max\\
\hline
 & Number of hives & 14.80 & 0.00 & 17.03 & 0.00 & 40.00\\
\cline{2-7}
 & Distance to edge (m) & 137.48 & 20.00 & 195.02 & 1.00 & 500.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 10.31 & 0.00 & 28.80 & 0.00 & 218.18\\
\cline{2-7}
 & Flower density (m$^2$) & 470.33 & 448.00 & 231.32 & 52.00 & 1684.00\\
\cline{2-7}
 & Pollen per stigma & 293.33 & 155.00 & 385.04 & 0.00 & 3891.00\\
\cline{2-7}
 & Plant density (m$^2$) & 3.77 & 3.77 & 0.48 & 1.79 & 5.02\\
\cline{2-7}
 & Plant vegetative mass (g) & 18.15 & 14.32 & 14.07 & 0.77 & 107.66\\
\cline{2-7}
 & Plant seed mass (g) & 6.87 & 5.46 & 5.97 & 0.01 & 47.90\\
\cline{2-7}
 & Harvest index (g/g) & 0.38 & 0.37 & 0.16 & 0.00 & 1.89\\
\cline{2-7}
 & Flowers per plant & 196.09 & 156.50 & 150.96 & 13.00 & 1094.00\\
\cline{2-7}
 & Pods per plant & 143.15 & 112.00 & 114.64 & 5.00 & 892.00\\
\cline{2-7}
 & Seeds per pod & 22.96 & 23.60 & 4.97 & 4.60 & 35.40\\
\cline{2-7}
\multirow{-13}{*}{\raggedright\arraybackslash Commodity} & Seed size (mg) & 2.74 & 2.73 & 0.80 & 0.39 & 5.35\\
\cline{1-7}
 & Distance to edge (m) & 162.70 & 100.00 & 146.18 & 3.00 & 400.00\\
\cline{2-7}
 & Distance to LCB shelter (m) & 33.51 & 31.00 & 24.63 & 2.00 & 190.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 112.79 & 24.00 & 187.30 & 0.00 & 1290.00\\
\cline{2-7}
 & LCB visitation (hr$^{-1}$) & 76.15 & 12.00 & 144.88 & 0.00 & 1272.00\\
\cline{2-7}
 & Bay Edge/Centre & 0.13 & 0.00 & 0.34 & 0.00 & 1.00\\
\cline{2-7}
 & Flower density (m$^2$) & 495.02 & 432.00 & 303.35 & 24.00 & 2686.40\\
\cline{2-7}
 & Pollen per stigma & 21.76 & 7.00 & 42.53 & 0.00 & 578.00\\
\cline{2-7}
 & Plant density (m$^2$) & 3.58 & 3.64 & 0.46 & 2.40 & 4.49\\
\cline{2-7}
 & Plant vegetative mass (g) & 30.32 & 25.19 & 21.16 & 1.18 & 144.32\\
\cline{2-7}
 & Plant seed mass (g) & 9.50 & 7.54 & 7.90 & 0.02 & 60.77\\
\cline{2-7}
 & Harvest index (g/g) & 0.32 & 0.33 & 0.15 & 0.00 & 1.21\\
\cline{2-7}
 & Flowers per plant & 461.32 & 362.50 & 326.59 & 26.00 & 2712.00\\
\cline{2-7}
 & Pods per plant & 299.41 & 244.50 & 207.68 & 10.00 & 1410.00\\
\cline{2-7}
 & Seeds per pod & 16.40 & 16.60 & 5.52 & 1.80 & 30.60\\
\cline{2-7}
\multirow{-15}{*}{\raggedright\arraybackslash Seed} & Seed size (mg) & 3.43 & 3.42 & 0.88 & 1.04 & 5.59\\
\hline
\end{tabular}

@@

During 2015, we recorded whether honey bees were top-working or side-working flowers (see also \citealp{free1973, free1983, mohr1988}).
Top-working bees landed on the top of the flower and inserted their proboscis down between the petals to access the nectaries of the flower, while side-working bees landed on the side of the flower and stole nectar by inserted their proboscis between the petals, avoiding contact with the stigma or anthers. 
Additionally, we recorded whether honey bees were pollen or nectar foragers (pollen foragers had a visible pollen load on their corbicula, while nectar foragers had none).

@@

\begin{table}
    \begin{tabular}{r|r|l|r|l}
     & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c}{Seed fields} \\ \cline{2-5}
    Taxon & Visits & \% & Visits & \% \\ \hline
    Honey bee & 470 & 53.5 & 4850 & 77.1 \\
    Fly & 222 & 25.3 & 74 & 0.878 \\
    Hover fly & 94 & 10.7 & 151 & 1.79 \\
    Other bee & 47 & 5.35 & 30 & 0.356 \\
    Bumble bee & 25 & 2.85 & 0 & 0 \\
    Butterfly & 16 & 1.82 & 0 & 0 \\
    Leafcutter bee & 4 & 0.456 & 1675 & 19.9 \\
    % \hline
    % Total & 828 & - & 6780 & - \\
    \end{tabular}
    \caption{Number of flower visitors recorded over a total of 44.8 hours of observation in commodity fields (2014 and 2015), and 46.9 hours of observation in the seed fields (2015 and 2016). ``Fly" refers to larger calyptrate muscoid flies (families Muscidae, Anthomyiidae, Caliphoridae), while ``Hover fly" refers to Syrphid flies. ``Other bee" included Halictid and Andrenid bees, while ``Bumble bee" was \textit{Bombus} spp. ``Butterfly" refers to all visiting Lepidopterans, mostly Pierids.}
    \label{tab:propVisitors}  
\end{table}

\begin{table}
\begin{tabular}{r|r|l|r|l|r|l}
               & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c|}{Seed fields (female bay)} & \multicolumn{2}{c}{Seed fields (male bay)} \\ \cline{2-7}
               & Top & Side & Top & Side & Top & Side           \\ \hline
Pollen forager & 44 & 2 & 12 & 0 & 115 & 0 \\
Nectar forager & 75 & 138 & 832 & 24 & 428 & 242 \\
% Total & 119 & 140 & 844 & 24 & 543 & 242
\end{tabular}
\caption[Foraging behaviours of honey bees on commodity and seed canola flowers]{Foraging behaviours of honey bees on commodity and seed canola flowers, recorded during 2015. ``Top" (top-working) indicates that the bee inserted their proboscis down between the petals from the top of the flower, while ``side" (side-working) indicates that the bee fed from the side of the flower and did not contact the anthers or stigma. Pollen foragers had pollen visible on their corbicula, while nectar foragers had none.}
\label{tab:sideWorking}
\end{table}

@@

\begin{tabular}{l|l|r|r|r|r|r|r|r|r|r}
\hline
Field Type & Parameter & Mean & SD & Z & median & Min & Max & p-value & N$_{eff}$ & $\hat{R}$\\
\hline
 & Intercept & -0.318 & 0.042 & -7.62 & -0.317 & -0.397 & -0.236 & 0.000 & 982 & 1.000\\
\cline{2-11}
 & Predicted Yield & 1.007 & 0.018 & 55.64 & 1.007 & 0.972 & 1.044 & 0.000 & 1044 & 1.000\\
\cline{2-11}
 & Sigma (field intercept) & 0.119 & 0.041 & 2.89 & 0.112 & 0.051 & 0.216 & 0.004 & 292 & 1.020\\
\cline{2-11}
 & Sigma (field slope) & 0.026 & 0.019 & 1.37 & 0.023 & 0.001 & 0.072 & 0.170 & 295 & 1.013\\
\cline{2-11}
 & Sigma (plot intercept) & 0.389 & 0.037 & 10.47 & 0.388 & 0.318 & 0.465 & 0.000 & 506 & 1.005\\
\cline{2-11}
 & Sigma (plot slope) & 0.169 & 0.017 & 9.86 & 0.168 & 0.135 & 0.204 & 0.000 & 556 & 1.006\\
\cline{2-11}
 & Sigma & 0.253 & 0.008 & 33.30 & 0.253 & 0.239 & 0.268 & 0.000 & 2002 & 1.000\\
\cline{2-11}
 & Correlation (Int:Slope field) & -0.400 & 0.448 & -0.89 & -0.525 & -0.944 & 0.626 & 0.372 & 660 & 1.005\\
\cline{2-11}
\multirow{-9}{*}{\raggedright\arraybackslash Commodity} & Correlation (Int:Slope plot) & -0.989 & 0.007 & -140.44 & -0.990 & -0.998 & -0.972 & 0.000 & 936 & 1.005\\
\cline{1-11}
 & Intercept & -0.210 & 0.072 & -2.90 & -0.210 & -0.348 & -0.066 & 0.004 & 738 & 1.007\\
\cline{2-11}
 & Predicted Yield & 0.856 & 0.025 & 34.62 & 0.856 & 0.806 & 0.904 & 0.000 & 672 & 1.008\\
\cline{2-11}
 & Sigma (field intercept) & 0.040 & 0.018 & 2.28 & 0.038 & 0.011 & 0.079 & 0.022 & 226 & 1.005\\
\cline{2-11}
 & Sigma (field slope) & 0.010 & 0.007 & 1.56 & 0.009 & 0.001 & 0.023 & 0.118 & 217 & 1.005\\
\cline{2-11}
 & Sigma (plot intercept) & 0.097 & 0.013 & 7.26 & 0.097 & 0.072 & 0.124 & 0.000 & 470 & 1.005\\
\cline{2-11}
 & Sigma (plot slope) & 0.032 & 0.005 & 5.83 & 0.032 & 0.021 & 0.043 & 0.000 & 379 & 1.006\\
\cline{2-11}
 & Sigma & 0.289 & 0.012 & 23.59 & 0.289 & 0.266 & 0.314 & 0.000 & 1218 & 1.001\\
\cline{2-11}
 & Correlation (Int:Slope field) & -0.470 & 0.436 & -1.08 & -0.616 & -0.946 & 0.603 & 0.281 & 457 & 1.005\\
\cline{2-11}
\multirow{-9}{*}{\raggedright\arraybackslash Seed} & Correlation (Int:Slope plot) & -0.902 & 0.038 & -23.81 & -0.909 & -0.954 & -0.808 & 0.000 & 486 & 1.007\\
\hline
\end{tabular}
\endgroup{}

\label{tab:totalYieldCoefs}
\end{table}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/FieldLocations.png}
    \caption{Map of sampled fields, showing locations of 29 commodity canola fields (14 during 2014, 15 during 2015), and 35 seed canola fields (15 during 2015, 20 during 2016). Seed canola is grown only in southern Alberta, while commodity canola is grown across both the northern and southern regions.}
    \label{fig:fieldMap}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{seedfieldBays.jpg}
    \caption[Hybrid seed field production field near Rainer, AB]{Hybrid seed field near Rainer, AB, showing the outlines of male and female bays in the foreground, with orange leafcutter bee shelters stationed throughout the field. The linear structure on the horizon is the central-pivot irrigation sprinkler.}
    \label{fig:seedfieldPhoto}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{seedfieldPlots.png}
    \caption[Plot arrangement for surveys in hybrid seed fields]{Plot arrangement for surveys in hybrid seed fields, showing hypothetical arrangement of leafcutter shelters ($\Delta$), and male-fertile (\Hermaphrodite) and female bays (\Female) at 5m from the edge of the field. Plots were placed along a transect (dashed line) from the field edge nearest to the set of honey bee hives. Plots were placed side-by-side in the male bay and edge of the female bay (``edge" plots), and at the 5m and 400m distances, an additional plot was placed in the centre of the female bay (``centre" plots). Note: this figure shows a small section of a much larger circular field.}
    \label{fig:seedfieldPlots}
\end{figure}

\begin{table}[h]
\caption{Summary of variables used in structural equation models.}
\centering
\begin{tabular}{l|l|r|r|r|r|r}
\hline
Field Type & Variable & Mean & Median & SD & Min & Max\\
\hline
 & Number of hives & 14.80 & 0.00 & 17.03 & 0.00 & 40.00\\
\cline{2-7}
 & Distance to edge (m) & 137.48 & 20.00 & 195.02 & 1.00 & 500.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 10.31 & 0.00 & 28.80 & 0.00 & 218.18\\
\cline{2-7}
 & Flower density (m$^2$) & 470.33 & 448.00 & 231.32 & 52.00 & 1684.00\\
\cline{2-7}
 & Pollen per stigma & 293.33 & 155.00 & 385.04 & 0.00 & 3891.00\\
\cline{2-7}
 & Plant density (m$^2$) & 3.77 & 3.77 & 0.48 & 1.79 & 5.02\\
\cline{2-7}
 & Plant vegetative mass (g) & 18.15 & 14.32 & 14.07 & 0.77 & 107.66\\
\cline{2-7}
 & Plant seed mass (g) & 6.87 & 5.46 & 5.97 & 0.01 & 47.90\\
\cline{2-7}
 & Harvest index (g/g) & 0.38 & 0.37 & 0.16 & 0.00 & 1.89\\
\cline{2-7}
 & Flowers per plant & 196.09 & 156.50 & 150.96 & 13.00 & 1094.00\\
\cline{2-7}
 & Pods per plant & 143.15 & 112.00 & 114.64 & 5.00 & 892.00\\
\cline{2-7}
 & Seeds per pod & 22.96 & 23.60 & 4.97 & 4.60 & 35.40\\
\cline{2-7}
\multirow{-13}{*}{\raggedright\arraybackslash Commodity} & Seed size (mg) & 2.74 & 2.73 & 0.80 & 0.39 & 5.35\\
\cline{1-7}
 & Distance to edge (m) & 162.70 & 100.00 & 146.18 & 3.00 & 400.00\\
\cline{2-7}
 & Distance to LCB shelter (m) & 33.51 & 31.00 & 24.63 & 2.00 & 190.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 112.79 & 24.00 & 187.30 & 0.00 & 1290.00\\
\cline{2-7}
 & LCB visitation (hr$^{-1}$) & 76.15 & 12.00 & 144.88 & 0.00 & 1272.00\\
\cline{2-7}
 & Bay Edge/Centre & 0.13 & 0.00 & 0.34 & 0.00 & 1.00\\
\cline{2-7}
 & Flower density (m$^2$) & 495.02 & 432.00 & 303.35 & 24.00 & 2686.40\\
\cline{2-7}
 & Pollen per stigma & 21.76 & 7.00 & 42.53 & 0.00 & 578.00\\
\cline{2-7}
 & Plant density (m$^2$) & 3.58 & 3.64 & 0.46 & 2.40 & 4.49\\
\cline{2-7}
 & Plant vegetative mass (g) & 30.32 & 25.19 & 21.16 & 1.18 & 144.32\\
\cline{2-7}
 & Plant seed mass (g) & 9.50 & 7.54 & 7.90 & 0.02 & 60.77\\
\cline{2-7}
 & Harvest index (g/g) & 0.32 & 0.33 & 0.15 & 0.00 & 1.21\\
\cline{2-7}
 & Flowers per plant & 461.32 & 362.50 & 326.59 & 26.00 & 2712.00\\
\cline{2-7}
 & Pods per plant & 299.41 & 244.50 & 207.68 & 10.00 & 1410.00\\
\cline{2-7}
 & Seeds per pod & 16.40 & 16.60 & 5.52 & 1.80 & 30.60\\
\cline{2-7}
\multirow{-15}{*}{\raggedright\arraybackslash Seed} & Seed size (mg) & 3.43 & 3.42 & 0.88 & 1.04 & 5.59\\
\hline
\end{tabular}

@@

In 2015, we recorded whether honey bees were top-working or side-working flowers (see also \citealp{free1973, free1983, mohr1988}).
Top-working bees landed on the top of the flower and inserted their proboscis down between the petals to access the nectaries of the flower, while side-working bees landed on the side of the flower and stole nectar by inserted their proboscis between the petals, avoiding contact with the stigma or anthers. 
Additionally, we recorded whether honey bees were pollen or nectar foragers (pollen foragers had a visible pollen load on their corbicula, while nectar foragers had none).

@@

\begin{table}[h]
  \caption{Number of flower visitors recorded over a total of 44.8 hours of observation in commodity fields (2014 and 2015), and 46.9 hours of observation in the seed fields (2015 and 2016). ``Fly" refers to larger calyptrate muscoid flies (families Muscidae, Anthomyiidae, Caliphoridae), while ``Hover fly" refers to Syrphid flies. ``Other bee" included Halictid and Andrenid bees, while ``Bumble bee" was \textit{Bombus} spp. ``Butterfly" refers to all visiting Lepidopterans, mostly Pierids.}
  \centering
    \begin{tabular}{r|r|l|r|l}
     & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c}{Seed fields} \\ \cline{2-5}
    Taxon & Visits & \% & Visits & \% \\ \hline
    Honey bee & 470 & 53.5 & 4850 & 77.1 \\
    Fly & 222 & 25.3 & 74 & 0.878 \\
    Hover fly & 94 & 10.7 & 151 & 1.79 \\
    Other bee & 47 & 5.35 & 30 & 0.356 \\
    Bumble bee & 25 & 2.85 & 0 & 0 \\
    Butterfly & 16 & 1.82 & 0 & 0 \\
    Leafcutter bee & 4 & 0.456 & 1675 & 19.9 \\
    % \hline
    % Total & 828 & - & 6780 & - \\
    \end{tabular}
    \label{tab:propVisitors}
\end{table}

\begin{table}[h]
\caption[Foraging behaviours of honey bees on commodity and seed canola flowers]{Foraging behaviours of honey bees on commodity and seed canola flowers, recorded during 2015. ``Top" (top-working) indicates that the bee inserted their proboscis down between the petals from the top of the flower, while ``side" (side-working) indicates that the bee fed from the side of the flower and did not contact the anthers or stigma. Pollen foragers had pollen visible on their corbicula, while nectar foragers had none.}
\begin{tabular}{r|r|l|r|l|r|l}
               & \multicolumn{2}{c|}{Commodity fields} & \multicolumn{2}{c|}{Seed fields (female bay)} & \multicolumn{2}{c}{Seed fields (male bay)} \\ \cline{2-7}
               & Top & Side & Top & Side & Top & Side           \\ \hline
Pollen forager & 44 & 2 & 12 & 0 & 115 & 0 \\
Nectar forager & 75 & 138 & 832 & 24 & 428 & 242 \\
% Total & 119 & 140 & 844 & 24 & 543 & 242
\end{tabular}
\label{tab:sideWorking}
\end{table}

@@

\begin{tabular}{l|l|r|r|r|r|r|r|r|r|r}
\hline
Field Type & Parameter & Mean & SD & Z & median & Min & Max & p-value & N$_{eff}$ & $\hat{R}$\\
\hline
 & Intercept & -0.318 & 0.042 & -7.62 & -0.317 & -0.397 & -0.236 & 0.000 & 982 & 1.000\\
\cline{2-11}
 & Predicted Yield & 1.007 & 0.018 & 55.64 & 1.007 & 0.972 & 1.044 & 0.000 & 1044 & 1.000\\
\cline{2-11}
 & Sigma (field intercept) & 0.119 & 0.041 & 2.89 & 0.112 & 0.051 & 0.216 & 0.004 & 292 & 1.020\\
\cline{2-11}
 & Sigma (field slope) & 0.026 & 0.019 & 1.37 & 0.023 & 0.001 & 0.072 & 0.170 & 295 & 1.013\\
\cline{2-11}
 & Sigma (plot intercept) & 0.389 & 0.037 & 10.47 & 0.388 & 0.318 & 0.465 & 0.000 & 506 & 1.005\\
\cline{2-11}
 & Sigma (plot slope) & 0.169 & 0.017 & 9.86 & 0.168 & 0.135 & 0.204 & 0.000 & 556 & 1.006\\
\cline{2-11}
 & Sigma & 0.253 & 0.008 & 33.30 & 0.253 & 0.239 & 0.268 & 0.000 & 2002 & 1.000\\
\cline{2-11}
 & Correlation (Int:Slope field) & -0.400 & 0.448 & -0.89 & -0.525 & -0.944 & 0.626 & 0.372 & 660 & 1.005\\
\cline{2-11}
\multirow{-9}{*}{\raggedright\arraybackslash Commodity} & Correlation (Int:Slope plot) & -0.989 & 0.007 & -140.44 & -0.990 & -0.998 & -0.972 & 0.000 & 936 & 1.005\\
\cline{1-11}
 & Intercept & -0.210 & 0.072 & -2.90 & -0.210 & -0.348 & -0.066 & 0.004 & 738 & 1.007\\
\cline{2-11}
 & Predicted Yield & 0.856 & 0.025 & 34.62 & 0.856 & 0.806 & 0.904 & 0.000 & 672 & 1.008\\
\cline{2-11}
 & Sigma (field intercept) & 0.040 & 0.018 & 2.28 & 0.038 & 0.011 & 0.079 & 0.022 & 226 & 1.005\\
\cline{2-11}
 & Sigma (field slope) & 0.010 & 0.007 & 1.56 & 0.009 & 0.001 & 0.023 & 0.118 & 217 & 1.005\\
\cline{2-11}
 & Sigma (plot intercept) & 0.097 & 0.013 & 7.26 & 0.097 & 0.072 & 0.124 & 0.000 & 470 & 1.005\\
\cline{2-11}
 & Sigma (plot slope) & 0.032 & 0.005 & 5.83 & 0.032 & 0.021 & 0.043 & 0.000 & 379 & 1.006\\
\cline{2-11}
 & Sigma & 0.289 & 0.012 & 23.59 & 0.289 & 0.266 & 0.314 & 0.000 & 1218 & 1.001\\
\cline{2-11}
 & Correlation (Int:Slope field) & -0.470 & 0.436 & -1.08 & -0.616 & -0.946 & 0.603 & 0.281 & 457 & 1.005\\
\cline{2-11}
\multirow{-9}{*}{\raggedright\arraybackslash Seed} & Correlation (Int:Slope plot) & -0.902 & 0.038 & -23.81 & -0.909 & -0.954 & -0.808 & 0.000 & 486 & 1.007\\
\hline
\end{tabular}
\label{tab:totalYieldCoefs}
\endgroup{}
\end{table}
